### 2021-11-23 README.Rmd
mild wording changes

Next is plot of the US personal expenditure over 5 categories and 5 years, and is a simple example of how wide format data can be used with `ggmatplot()`. Note how the expenditure categories to be used on the x axis is used as vector x, and the expenditure values is used in wide format as matrix y - with its columns corresponding to the grouping structure.

>>>>

Next is plot of the US personal expenditure over 5 categories and 5 years, and is a simple example of how wide format data can be used with `ggmatplot()`. Note how the expenditure categories to be used on the x axis is used as vector `x`, and the expenditure values is used in wide format as matrix `y` - with its columns corresponding to the grouping structure.
